Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-13 krs-survey.tex
Mention Levesque2008 in Previous Work

To the extend of our knowledge, no previous published work attempt to build a
typology of cognitive abilities strictly related to knowledge in the context of
service robotics.

>>>>

A large part of our proposal is build as a comprehensive synthesis of
classification and analysis found in the literatture. This synthesis is focused
on cognitive abilities strictly related to knowledge manipulation, in the
context of service robotics.

Levesque and Lakemeyer~\cite{Levesque2008} present in a chapter on Cognitive
Robotics several characteristics of knowledge representation systems for
robots, stressing the need of representing the dynamics of the world.  Sensing
is included in the knowledge representation via fluents; they introduce the
idea of \emph{possible worlds} to represent distinct parallel mental models;
action representation and reasoning about tasks is discussed in the context of
situation calculus; open world vs. closed world approaches are both mentioned.
They also discuss how robot programming and knowledge representation can be
related. We integrate most of these items in our typology.
